---
format: gfm
editor: visual
editor_options: 
  chunk_output_type: console
execute:
  echo: false
  warning: false
---

# biomeddashboard-neuro-trials

This repository is part of the [ScholCommLab-led project "Biomed OS Dashboard"](https://docs.google.com/document/d/18zr1QBbvstYkXOXK2l-2OUyVhWExH54eeW8BGimYN98/). It uses [data on a sample of The Neuro's publication records](https://www.dropbox.com/s/lxjsihhzys7h6r7/cleaned_y2021_oa_info_109.csv?dl=0) and builds off [code developed for QUEST's project "IntoValue"](https://github.com/maia-sh/intovalue-data).

Here, we evaluate The Neuro's publications for the presence of clinical trial registration numbers (TRNs) in their PubMed abstracts and metadata ("secondary identifier" field). Methods are described in detail [Salholz-Hillel et al. 2022](https://doi.org/10.1177/17407745221087456).

```{r, setup}
library(dplyr)

query_logs <- loggit::read_logs(here::here("queries.log"))

get_latest_query <- function(query, logs) {
  logs |> 
  filter(log_msg == query) |> 
    arrange(desc(timestamp)) |> 
    slice_head(n = 1) |> 
    pull(timestamp) |> 
    as.Date.character()
}

publications <- readr::read_csv(here::here("data", "raw", "neuro-validated-pubs.csv"))
trns <- readr::read_csv(here::here("data", "processed", "trn", "trn-combined.csv"))
```

PubMed records were downloaded on `r get_latest_query("PubMed", query_logs)`.

## Results

In the sample of `r nrow(publications)` The Neuro publications, we found `r nrow(trns)` TRNs in the PubMed abstracts and metadata of `r n_distinct(trns$pmid)` publications.

Of PubMed records with TRNs, most had TRNs in both the abstract and metadata:

```{r}
count(trns, has_trn_secondary_id, has_trn_abstract) |> 
  arrange(desc(n)) |> 
  knitr::kable()
```

ClinicalTrials.gov was by far the most common registry:

```{r}
count(trns, registry) |> 
  arrange(desc(n)) |> 
  knitr::kable()
```

Of PubMed records with TRNs, most include a single TRN:

```{r}
trns |> 
count(pmid, name = "n_trns") |> 
  count(n_trns, name = "n_pmids") |> 
  knitr::kable()
```

Get the csv of TRNs here!
